Discussion Draft

### 2020-04-13 doc/Discussion.rmd
small changes for adding to discussion
rough rough draft for conseq of chromatin str

@@

>>>>

# significance, consequences
# weak evidence of sex differences in chromatin organization, mice-humans have a similar direction -- but At opposite -- not much empiracal evidence. (more data needed)

# a consequence of these sex differences for the chromatin organization is -- has an outcome of different effects on interference strenth measured in genetic map space -- for a given chromosome, chromatin organization of longer axis will result in shorter loops (emenating off the central axis)

#1. interference signal travels through the SC / axis
#since interference strength is mediated through the SC / chromatid axis
# in both sexes interference strength discribed in units SC (axis) -- will be more conserved within and between species.

#2. the tethering of loops to the axis is highly conserved - so variable chromatin organization for a given chromosome of constant size stems from varying the size of the loops and length of the axis.

#3 when interference strength of a given unit of SC/axis / physical area -- is translated into base pairs (Mb), the chromosome organization with larger loops (smaller axis length) will have stronger interference -since more base pairs are passed/sequestered in the DNA loops per unit of SC/axis.

#4.ppl should care -- this is an important aspect of -- how sexual dimorphism in recombination /linkage maps has been charaecterized -- but due to a lack of cytological evidence in both sexes /linking this to chromatin organization has only been done for a handful of species (mice, human, At? Dourad)

@@

1. interference signal travels through the SC / axis
since interference strength is mediated through the SC / chromatid axis
 in both sexes interference strength discribed in units SC (axis) -- will be more conserved within and between species.

2. the tethering of loops to the axis is highly conserved - so variable chromatin organization for a given chromosome of constant size stems from varying the size of the loops and length of the axis.

3 when interference strength of a given unit of SC/axis / physical area -- is translated into base pairs (Mb), the chromosome organization with larger loops (smaller axis length) will have stronger interference -since more base pairs are passed/sequestered in the DNA loops per unit of SC/axis.

4.ppl should care -- this is an important aspect of -- how sexual dimorphism in recombination /linkage maps has been charaecterized -- but due to a lack of cytological evidence in both sexes /linking this to chromatin organization has only been done for a handful of species (mice, human, At? Dourad)
